Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 dropping.tex
Spacing around tables/figures.
Edits from Andrew's comments.

% Run-time monitoring overview
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/monitoring_architecture.pdf}
    \vspace{-0.2in}
    \caption{Overview of run-time monitoring architecture.}
    \label{fig:dropping.overview} 
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

% Example monitor
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/example_full.pdf}
    \caption{Example of array bounds check monitor.}
    \label{fig:dropping.example_full}
    \vspace{-0.1in}
  \end{center}
\end{figure*}

@@

Note that this monitoring is performed automatically and transparently with
almost no modification needed to the main program. The only modification to
the main program that is needed is to initially set metadata, such as setting
the base and bounds addresses on a {\tt malloc} call for array bounds check.
The propagation and checks of the metadata occur automatically as
instructions are forwarded to the monitor.
Here, we have shown the dynamic sequence of operations executed by the monitor but
the actual static code consists of a set of instructions to be run for each
possible instruction type (load, store, etc.). Only instruction types relevant
for the particular monitoring scheme are forwarded.

@@

% Example with invalidation
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/example_invalid.pdf}
    \caption{Example of using invalidation information to prevent false positives.}
    \label{fig:dropping.example_invalid}
    \vspace{-0.1in}
  \end{center}
\end{figure*}

@@

% Dataflow engine high-level
\begin{figure}
  \begin{center}
    \vspace{-0.1in}
    \includegraphics[width=\columnwidth]{figs/dataflow_overview.pdf}
    \vspace{-0.2in}
    \caption{Hardware support for dropping.}
    \label{fig:dropping.dataflow_overview}
    \vspace{-0.2in}
  \end{center}
\end{figure}

@@

% Detailed architecture of dataflow engine
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/dataflow_architecture.pdf}
    \vspace{-0.1in}
    \caption{Hardware architecture of the dataflow engine.}
    \label{fig:dropping.dataflow} 
    \vspace{-0.1in}
  \end{center}
\end{figure*}

@@

% Null filtering code example
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/example_null_filtering.pdf}
    \vspace{-0.2in}
    \caption{Example of using information about null metadata to filter monitoring events.}
    \label{fig:dropping.example_null} 
    \vspace{-0.1in}
  \end{center}
\end{figure}

>>>>

% Run-time monitoring overview
\begin{figure}
  \begin{center}
    \vspace{0.1in}
    \includegraphics[width=\columnwidth]{figs/monitoring_architecture.pdf}
    \vspace{-0.2in}
    \caption{Overview of run-time monitoring architecture.}
    \label{fig:dropping.overview} 
    \vspace{-0.3in}
  \end{center}
\end{figure}

@@

% Example monitor
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/example_full.pdf}
    \caption{Example of array bounds check monitor.}
    \label{fig:dropping.example_full}
    \vspace{-0.2in}
  \end{center}
\end{figure*}

@@

Note that this monitoring is performed automatically and transparently with
almost no modification needed to the main program. The only modification to
the main program that is needed is to initially set metadata, such as setting
the base and bounds addresses on a {\tt malloc} call for array bounds checking.
The propagation and checks of the metadata occur automatically as
instructions are forwarded to the monitor.
Here, we have shown the dynamic sequence of operations executed by the monitor, but
the actual static code consists of a set of instructions to be run for each
possible instruction type (load, store, etc.). Only instruction types relevant
for the particular monitoring scheme are forwarded.

@@

% Example with invalidation
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/example_invalid.pdf}
    \caption{Example of using invalidation information to prevent false positives.}
    \label{fig:dropping.example_invalid}
    \vspace{-0.2in}
  \end{center}
\end{figure*}

@@

% Dataflow engine high-level
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/dataflow_overview.pdf}
    \vspace{-0.2in}
    \caption{Hardware support for dropping.}
    \label{fig:dropping.dataflow_overview}
    \vspace{-0.3in}
  \end{center}
\end{figure}

@@

% Detailed architecture of dataflow engine
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/dataflow_architecture.pdf}
    \vspace{-0.0in}
    \caption{Hardware architecture of the dataflow engine.}
    \label{fig:dropping.dataflow} 
    \vspace{-0.3in}
  \end{center}
\end{figure*}

@@

% Null filtering code example
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/example_null_filtering.pdf}
    \vspace{-0.1in}
    \caption{Example of using information about null metadata to filter monitoring events.}
    \label{fig:dropping.example_null} 
    \vspace{-0.2in}
  \end{center}
\end{figure}

### 2015-01-05 introduction.tex
Edits from Andrew's comments.

Although partial monitoring comes at the cost of reduced monitoring coverage (i.e.,
effectiveness), this can still be useful in many scenarios.
For example, partial
monitoring can enable a level of protection even for systems where the full
monitoring overhead is too high. This is especially true for energy- or
power-constrained systems or soft real-time systems where the monitoring
overhead should not exceed energy/power limits or real-time deadlines.
Additionally, partial monitoring can be used for debugging purposes
especially in the context of sampling-based or cooperative debugging techniques
which expect low coverage per run but use a large number of runs and users to
collect debugging information~\cite{liblit-pldi05, chilimbi-asplos04,
greathouse-cgo11}.

>>>>

Although partial monitoring comes at the cost of reduced monitoring coverage (i.e.,
effectiveness), this can still be useful in many scenarios.
For example, partial
monitoring can enable a level of protection even for systems where the full
monitoring overhead is too high. This is especially true for energy- or
power-constrained systems or soft real-time systems where the monitoring
overhead should not exceed energy/power limits or real-time deadlines.
Additionally, partial monitoring can be used for sampling-based or cooperative debugging techniques
which expect low coverage per run but use a large number of runs and users to
collect debugging information~\cite{liblit-pldi05, chilimbi-asplos04,
greathouse-cgo11}.
